\documentclass[defaultstyle,11pt]{mythesis}

\usepackage{hyperref}		% PDF hyperreferences??


% packages just included...did not check for duplications or if they
% are actually required!
\RequirePackage{xspace}
\usepackage{float}
\usepackage{rotating}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{syntonly}
\usepackage{stmaryrd}
%\usepackage{subfigure}
\usepackage{wrapfig}
\usepackage{import}
\usepackage{enumerate}
\usepackage{amsmath,amssymb,amsfonts}
\pagestyle{plain}
\usepackage{times}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{balance}
\usepackage[sort]{cite}
%\usepackage[cmex10,fleqn]{amsmath}
\usepackage{array}
\usepackage{booktabs,siunitx}
\usepackage{url}
% traj_opt
\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,decorations,decorations.pathmorphing,positioning,fit,automata,shapes,snakes,patterns}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{subfig}
\usepackage{color}
\usepackage{xcolor,colortbl}
\usepackage{microtype}
\usetikzlibrary{arrows,backgrounds,positioning,fit,automata,shapes,snakes,patterns}
\usetikzlibrary{arrows,backgrounds,decorations,decorations.pathmorphing,positioning,fit,automata,shapes,snakes,patterns}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage{nameref}

% symex
\usepackage{framed}
\usepackage{ragged2e}
\usepackage{varwidth}
\usetikzlibrary{arrows,backgrounds,positioning,fit,automata,shapes,snakes,patterns}
\usetikzlibrary{arrows,backgrounds,decorations,decorations.pathmorphing,positioning,fit,automata,shapes,snakes,patterns}
\usetikzlibrary{shapes.geometric, arrows, positioning, calc, matrix}
% \tikzset{block/.style = {draw, fill=blue!20, rectangle,
%                          minimum height=3em, minimum width=6em},
%         sum/.style = {draw, fill=blue!20, circle, node distance=1cm},
%         input/.style = {coordinate},
%         output/.style = {coordinate},
%         pinstyle/.style = {pin edge={to-,thin,black}}
% }

%\usepackage{siunitx}
\usepackage{listings}

% \makeatletter
% \def\url@mystyle{%
%   %\@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
%   \@ifundefined{selectfont}{\def\UrlFont{\mathtt}}{\def\UrlFont{}}}
%   %\@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small}}}
% \makeatother
% %\urlstyle{mystyle}
% \urlstyle{rm}


\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Reachability Analysis of Cyber-Physical Systems using Symbolic-Numeric Techniques}

\author{Aditya Krishna}{Zutshi}

\otherdegrees{B.E., Manipal University, 2007 \\
	      M.S., University Colorado, 2011}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., Electrical Engineering}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
{Electrical, Computer, and Energy Engineering}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{Sriram Sankaranarayanan}			%  #2 {name}
        %\reader{}{}		%  3rd person to sign thesis
        \reader{Prof.\;Fabio Somenzi}		%  3rd person to sign thesis
        \readerThree{Prof.\;Bor-Yuh Evan Chang}		%  2nd person to sign thesis
        \readerFour{Dr.\;Jyotirmoy V. Deshmukh}		%  3rd person to sign thesis
        \readerFive{Dr.\;James Kapinski}		%  3rd person to sign thesis

\abstract{  \OnePageChapter	% because it is very short

    In this thesis, we address the problem of reachability analysis in
    cyber-physical systems. These are systems engineered by
    interfacing computational components with the physical world. They
    provide partially or fully automated safety-critical services in
    the form of medical devices, autonomous vehicles, avionics and
    power systems.

    We propose techniques to reason about the reachability of such
    systems, and provide methods for falsifying their safety
    properties. We model the cyber component as a software program and
    the physical component as a hybrid dynamical system. Unlike model
    based analysis, which uses either a purely symbolic or a numerical
    approach, we argue in favor of using a combination of the two. We
    justify this by noting that the software program running on a
    computer is completely specified and has precise semantics. In
    contrast, the model of the physical system is only an
    approximation. Hence, we treat the former as a white box, but
    treat the latter as a black box.

    Using symbolic methods for the cyber components and numerical
    methods for hybrid systems, we carefully capture the complex
    behaviors of software programs and circumvent the difficulty in
    analyzing complex models developed through first principles. To
    combine the two techniques, we use a Counterexample Guided
    Abstraction Refinement (CEGAR) framework. Furthermore, we explore
    learning techniques like regression and piecewise affine modeling
    to estimate and represent black box hybrid dynamical systems for
    the purpose of falsification.

    We use prototype implementations to demonstrate the effectiveness
    of presented ideas. Using non-trivial benchmarks, we compare their
    performance against the state of the art. We also comment on their
    applicability and discuss ideas for further improvement.



    %% OLD
%    In this thesis, we addresses the problem of reachability analyses
%    in cyber-physical systems. These systems are the result of cyber
%    components interacting with the physical world. They provide
%    partially or fully automated safety-critical services in the form
%    of medical devices, autonomous vehicles, avionics and power
%    systems.
%    %but not limited to health care as medical devices, personal and
%    %public transportation as critical safety features in cars,
%    %auto-pilots in airplanes, and, in managing sensitive
%    %infrastructure like power plants.
%
%    We propose techniques to reason about the reachability of such
%    systems, in order to provide methods for falsifying their safety
%    properties. We model the cyber component as a software program and
%    the physical component as a hybrid dynamical system. Unlike model
%    based analysis techniques which use either a purely symbolic or a
%    numerical approach, we argue in favor of using the combination of
%    the two.
%    %We justify this by highlighting the differences in the two models
%    %available in practice.
%    To elaborate, the completely specified software program running on
%    a microprocessor has precise semantics. In contrast, the physical
%    system is only approximately modeled in practice. Hence, we use
%    white-box techniques for the former, but treat the latter as a
%    black-box.  This allows us to carefully capture the complex
%    behaviors of softwares and circumvent the difficulty in analyzing
%    complex models developed through first principles.
%
%    We use symbolic techniques for the cyber components and propose
%    numerical techniques for hybrid systems. We then put forth a
%    Counterexample Guided Abstraction Refinement (CEGAR) framework to
%    combine the two techniques and provide a procedure to falsify
%    safety properties of the system. Furthermore, we explore learning
%    techniques like regression and piecewise affine modeling to
%    estimate and represent relevant symbolic information required to
%    falsify the property.
%
%    We use prototype implementations to demonstrate the effectiveness
%    of presented ideas. We use non-trivial benchmarks to compare their
%    performance against the state of the art. We also comment on their
%    applicability and discuss ideas for further improvement.

}
\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\newtheorem{example}{Example}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{proof}{Proof}[section]
%\newtheorem{theorem}{Theorem}[section]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input macros.tex
\input generic.macros.tex
\input specific.macros.tex


\include{intro}
\include{prelims}
\include{segtrajs}
\include{abstractions}
\include{symex}
\include{implementation}
\include{relational}
\include{conclusion}

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
%\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
% \appendix
% \include{appendixA.tex}
% \include{appendixB.tex}

\end{document}
